Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-07-04 paper/manuscript.Rmd
Specify NEE content type
Minimum proceedings B format structure

**Short title:** Competition for pollination vs. facilitation

<!-- **Keywords:** `r keywords` -->

<!-- **Type of article:** Primary research article -->

@@

**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.

@@

**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication.

@@

**Competing interests:** The authors have declared that no competing interests exist.

@@

@@

>>>>

<!-- **Short title:** Competition for pollination vs. facilitation -->

**Content type:** Research article.

@@

<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->

@@

<!-- **Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. -->

@@

<!-- **Competing interests:** The authors have declared that no competing interests exist. -->

@@

**Keywords:** `r keywords`

@@

# Funding
